Chord: A Versatile Platform for Program Analysis

### 2011-03-11 main/doc/chord_sysprops.tex
refactoring: moved chord.analyses.XYZ (where XZY is field, type, method, etc.) and all other factual domains/relations to chord.analyses.facts.XYZ to reduce cluttering in package chord.analyses

\noindent \code{chord.instr.kind}
\begin{quote}
{\bf Type:} {\tt [offline|online]}  \\
{\bf Description:} The kind of bytecode instrumentation.  The choices are offline and load-time.  \\
{\bf Default value:} {\tt offline}
\end{quote}

\noindent \code{chord.trace.kind}
\begin{quote}
{\bf Type:} {\tt [none|full|pipe]}  \\
{\bf Description:} The medium to store dynamic traces (none, regular file, or POSIX pipe).  \\
{\bf Default value:} {\tt full}
\end{quote}

\noindent \code{chord.trace.block.size}
\begin{quote}
{\bf Type:} int \\
{\bf Description:} Number of bytes to read/write in a single operation from/to the dynamic trace file. \\
{\bf Default value:} {\tt 4096}
\end{quote}

>>>>

\noindent \code{chord.instr.kind}
\begin{quote}
{\bf Type:} {\tt [offline|online]}  \\
{\bf Description:} The kind of bytecode instrumentation.  The choices are offline and online (load-time).  \\
{\bf Default value:} {\tt offline}
\end{quote}

\noindent \code{chord.trace.kind}
\begin{quote}
{\bf Type:} {\tt [full|pipe]}  \\
{\bf Description:} The medium by which an event-generating JVM and an event-handling JVM communicate in a dynamic analysis.  The choices are regular file and POSIX pipe.  \\
{\bf Default value:} {\tt full} 
\end{quote}

\noindent \code{chord.trace.block.size}
\begin{quote}
{\bf Type:} int \\
{\bf Description:} Number of bytes to read/write in a single operation from/to the event file used by a multi-JVM dynamic analysis. \\
{\bf Default value:} {\tt 4096}
\end{quote}
